plyr: Split-Apply-Combine for Mortals

### 2013-12-10 _knitr-posts/2013-12-01-plyr.Rmd
Fix link in plyr post

*Along with my [earlier post](http://localhost:4000/2013/10/19/reshape.html) on the `reshape2` package, I will continue to post my course notes from Data Wrangling and Visualization in R, a graduate-level course I co-taught last semester at Simon Fraser University.*

>>>>

*Along with my [earlier post](http://seananderson.ca/2013/10/19/reshape.html) on the `reshape2` package, I will continue to post my course notes from Data Wrangling and Visualization in R, a graduate-level course I co-taught last semester at Simon Fraser University.*
